Breeding bird indicators

### 2023-10-19 DRAFT_birdIndicators.Rmd
A bit on data analysis
to be continued...

## Analyses
### Data sets
<!-- Text here -->

#### Monitoring data from "Hekkefuglovervåkingen"
<!-- Text here -->

#### PECBMS Trim results from predecessor monitoring programme
<!-- Text here -->

>>>>

## Analyses
### Data sets
All data used are gathered under the Norwegian common breeding bird monitoring scheme (Hekkeguglovervåking in Norwegian; formely named TOV-E). For the calculation of multi-species indicators (MSI) of farmland and forest habitats, however, a longer dataset is used by combininng data from the 'predecessor monitoring programme', whic ran from 1995 to 2008.

#### Monitoring data from "Hekkefuglovervåkingen"
The route-based data are compiled after each breeding season and stored at NINA's database. The route-based data are then used to calculate the long-term trends (since 2008) in abundance for XX species, which have sufficient data to properly estimate the yearly abundance indices at a National scale.

#### PECBMS Trim results from predecessor monitoring programme
The abundance indices generated by TRIM using data from the predecessor scheme are stored in different repositories. These remain unchanged as this programme was discontinued in 2008 and no new data are being collected.
